---
title: "Assignment 3"
author: "Max Wagner"
date: "February 19, 2015"
header-includes:
   - \usepackage{bbm}
output:
  pdf_document: default
  html_document:
    highlight: espresso
    theme: flatly
---
***

####PS1.

####1.

The matrix in this case will looks like the following in row echelon form. In this case there are 4 non-zero rows, so the rank is 4. We can check in R with `rankMatrix()`.

```{r}
library(Matrix)
matrix <- matrix(c(1,-1,0,5,2,0,1,4,3,1,-2,-2,4,3,1,-3), nrow = 4)
matrix(c(1,0,0,0,2,2,0,0,3,4,-4,0,4,7,-5/2,9/8), nrow = 4)
```


```{r}
rankMatrix(matrix, method = "qr")[1] #using build in
```

####2.

`n` would be the maximum rank. Assuming the matrix is non-zero the minimum rank would be 1.

####3.

Rows 2 and 3 are eliminated, leaving 2 zero rows. The rank is 1.

```{r}
matrix <- matrix(c(1,0,0,2,0,0,1,0,0), nrow = 3);matrix
rankMatrix(matrix, method = "qr")[1]
```

####PS2

####1.

Solve for the determinant first.

$$
det(
\begin{bmatrix}
  1 & 2 & 3 \\
  0 & 4 & 5 \\
  0 & 0 & 6
\end{bmatrix}
-
\begin{bmatrix}
  \lambda & 0 & 0 \\
  0 & \lambda & 0 \\
  0 & 0 & \lambda
\end{bmatrix}
) = 0
$$

$$
det(
\begin{bmatrix}
  1-\lambda & 2 & 3 \\
  0 & 4-\lambda & 5 \\
  0 & 0 & 6-\lambda
\end{bmatrix}
) = 0
$$

$$
(1-\lambda)(4-\lambda)(6-\lambda) = 0
$$

Which gives the characteristic polynomial as the following, and three eigenvalues of 1, 4, and 6.

$$
-\lambda^{3}+11\lambda^{2}-34\lambda+24
$$

The eigenvalues plug in to give the following three equations:

$$
\begin{bmatrix}
  1-1 & 2 & 3 \\
  0 & 4-1 & 5 \\
  0 & 0 & 6-1
\end{bmatrix}
*
\begin{bmatrix}
  v_{1} \\
  v_{2} \\
  v_{3}
\end{bmatrix}
= 0
$$

$$
\begin{bmatrix}
  1-4 & 2 & 3 \\
  0 & 4-4 & 5 \\
  0 & 0 & 6-4
\end{bmatrix}
*
\begin{bmatrix}
  v_{1} \\
  v_{2} \\
  v_{3}
\end{bmatrix}
= 0
$$

$$
\begin{bmatrix}
  1-6 & 2 & 3 \\
  0 & 4-6 & 5 \\
  0 & 0 & 6-6
\end{bmatrix}
*
\begin{bmatrix}
  v_{1} \\
  v_{2} \\
  v_{3}
\end{bmatrix}
= 0
$$

Which then give eigenvectors of:

$$
\begin{bmatrix}
  1 \\
  0 \\
  0
\end{bmatrix}
,
\begin{bmatrix}
  1 \\
  3/2 \\
  0
\end{bmatrix}
,
\begin{bmatrix}
  1 \\
  25/16 \\
  5/8
\end{bmatrix}
$$