---
title: "Assignment 9"
author: "Max Wagner"
date: "March 28, 2016"
output:
  pdf_document: default
  html_document:
    highlight: espresso
    theme: flatly
header-includes: \usepackage{bbm}
---
***

###PS1

1.

A function to sample from the antiderivative of the distribution.

```{r}
invcdfgen <- function(x) {
  if (x <= 1 && x >= 0) {
    if (x <= .5) {
      return (sqrt(2 * x))
    } else {
      return (2 - sqrt(2 * (1 - x)))
    }
  }
}
```

2.

And now a function for the second section using antiderivatives again

```{r}
invcdfgen2 <- function(x) {
  if (x <= 1 && x >= 0) {
    if (x <= .5) {
      return (1 - sqrt(1 - 2 * x))
    } else {
      return (1 + sqrt(2 * x - 1))
    }
  }
}
```

3.

Sample from part 1:

```{r, warning=FALSE}
library(ggplot2)
sample.p1 <- sapply(runif(100000), invcdfgen)
qplot(sample.p1, geom = "histogram", bins = 100)
```

And a sample from part 2:

```{r, warning=FALSE}
sample.p2 <- sapply(runif(100000), invcdfgen2)
qplot(sample.p2, geom = "histogram", bins = 100)
```

4.

Just going to put n into a replicate function for this part:

```{r}
centralcalc <- function(n, PDF) {
  qplot(replicate(n, mean(sapply(runif(1000), PDF))))
}
```

And now testing it out with both functions:

```{r, cache=TRUE}
centralcalc(1000, invcdfgen)
centralcalc(1000, invcdfgen2)
```

5.

And trying with n = 20 to see how the CLT works. The graphs will not look perfect as the number of samples is fairly low.

```{r}
centralcalc(20, invcdfgen)
centralcalc(20, invcdfgen2)
```