---
title: "Assignment 6"
author: "Max Wagner"
date: "March 7, 2016"
header-includes:
   - \usepackage{bbm}
output:
  pdf_document: default
  html_document:
    highlight: espresso
    theme: flatly
---
***

####PS1.

Storing and displaying A, X, and Y:

```{r}
A <- matrix(c(-1,1,0,1,3,-2,5,0,1), nrow = 3);A
X <- A %*% t(A);X
Y <- t(A) %*% A;Y
```

Getting and printing eigenvalues/vectors of X and Y:

```{r}
x.eigen <- eigen(X);x.eigen
y.eigen <- eigen(Y);y.eigen
```

Getting the singular, left singular, and right singular values of A using `svd()`:

```{r}
a.svd <- svd(A)
a.svd$d
a.svd$u
a.svd$v
```

We can compare the two sets of singular vectors with the eigenvectors of X and Y. If the comparison works, they should be the same(can be negative).

For X:

```{r}
x.eigen$vectors
a.svd$u
```

For Y:

```{r}
y.eigen$vectors
a.svd$v
```

And finally for the singular values:

```{r}
x.eigen$values
y.eigen$values
a.svd$d ^ 2
```

####PS2

First step is to write a function to find the inverse of a matrix.

```{r}
myinverse <- function(A) {
  # Takes matrix A, and returns the inverse(B).
  
  if (det(A) != 0) { #checking for 0 determinant
    B <- matrix(data = NA,nrow = dim(A)[1], ncol = dim(A)[2])
    for (i in 1:dim(A)[1]) {
      for (j in 1:dim(A)[2]) {
        B[i,j] <- -1^(i+j) * det(A[-i,-j])
      }
    }
    return(t(B) / det(A))
  }
}
```

Let's test with the matrix from the first problem set.

```{r}
B <- myinverse(A)
A %*% B
```

The test for matrix A seems a bit off, but the inverse function itself seems to work fine.






